### 2019-02-14 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
I still don't have correct references...
Done for polishing references.

Efficient Medium Access (MAC) policies allow devices to avoid interfering traffic and can significantly reduce the spectrum contention problem in unlicensed bands.
As end-devices battery life is a key constraint of IoT networks,
this leads to IoT protocols using as low signaling overhead as possible and simple ALOHA-based mechanisms.
%
In this Section, we analyze the performance of Multi-Armed Bandits (MAB) algorithms, used in combination with a time-frequency slotted ALOHA-based protocol.
We consider the Upper-Confidence Bound (\UCB) \cite{Auer}, and the Thompson-Sampling (TS) algorithms \cite{Thompson33,AgrawalGoyal11,
Kaufmann12}.
% Both algorithms have already been applied with success, for Opportunistic Spectrum Access \cite{Jouini} and recently for multi-users Cognitive Radio problems \cite{Toldov}.

MAB learning has already been proposed in Cognitive Radio (CR) \cite{Haykin}, and in particular, for sensing-based Dynamic Spectrum Access (DSA) in licensed bands \cite{Jouini}.
For example, \cite{Jouini} presents the OSA setting, and \cite{Maghsudi} shows how MAB learning can be applied for small cell management in licensed 5G networks.
Recently, TS and \UCB{} algorithms have been used for improving the spectrum access in (unlicensed) WiFi networks \cite{Toldov}, and the \UCB{} algorithm was used in a unlicensed and frequency- and time-slotted IoT network \cite{Bonnefoi}.
Many recent works show that MAB algorithms work well for real-world radio signal.
However, even with only one dynamic user using the learning algorithm, the background traffic or the traffic of the other devices is never really stationary or \emph{i.i.d} (independent and identically distributed).
In recent works like \cite{Bonnefoi}, several devices are using bandit algorithms, and the assumptions made by the stochastic bandit algorithms are not satisfied: as several agents learn simultaneously, their behavior is neither stationary nor \emph{i.i.d}.
As far as we know, we provide the first study to confirm robustness of the use of stochastic bandit algorithms for decision making in IoT networks with a large number of intelligent devices in the network, which makes the environment not stationary at all, violating the hypothesis required for mathematical proofs of bandit algorithms convergence and efficiency.

@@

% We now present the stochastic Multi-Armed Bandit (MAB) model,
% and the two stochastic MAB algorithms used in our experiments \cite{bubeck2012regret}.
While the stochastic MAB model has been used to describe some aspects of Cognitive Radio systems, it is in principle not suitable for our IoT model, due to the non-stationarity of the channels occupancy caused by the learning policy used by dynamic objects.
%Quite surprisingly, we will show in our experiments of Section~\ref{sub:41:numericalResults} that two algorithms inspired by the stochastic bandit modeling, UCB1 and Thompson Sampling, perform well even for coordinating multiple smart devices.

%This section presents the formalism of the Multi-Armed Bandit (MAB) problem, as introduced by \cite{LaiRobbins85}, and two classical algorithms designed to tackle its simplest version (stochastic MAB), \UCB{} from \cite{Auer} and Thompson Sampling from \cite{Thompson33,Kaufmann12}.
%For more details, \cite{bubeck2012regret} is an excellent review.

@@

% In a Cognitive Radio application, arms model the \emph{channels}, and players are the \emph{dynamic end-devices}.
% For example in the classical OSA setting with sensing \cite{Jouini}, a single dynamic device (a player) sequentially tries to access channels (the arms), and collects a reward of 1 if the channel is available %(as there is no primary user, we can assume the transmission to be successful),
% and 0 otherwise. So rewards represent the \emph{availability} of channels, and
% the parameter $\mu_k$ represents the mean availability of channel $k$.

@@

\paragraph{\emph{Adversarial} bandit algorithms?}
% \todo[inline]{Explain that we also tried adversarial algorithms ($\mathrm{Exp}3$), and it was working but less efficiently than \UCB{} and Thompson Sampling. Maybe add it on some curve?}
Instead of using MAB algorithms assuming a stochastic hypothesis on the system, we could try to use MAB algorithms designed to tackle a more general problem, that makes no hypothesis on the interfering traffic.
The \emph{adversarial MAB} algorithms is a broader family, and a well-known and efficient example is the $\mathrm{Exp}3$ algorithm \cite{bubeck2012regret}.
Empirically, the $\mathrm{Exp}3$ algorithm turned out to perform worse than both \UCB{} and TS in the same experiments.
%(see Section \ref{sub:41:numericalResults}).
Contrarily to the two stochastic algorithms, the use of $\mathrm{Exp}3$ is correctly justified, even in the non-stationary and non-\emph{i.i.d}, as its performance guarantee are true in \emph{any} setting.
But it is not so surprising that it performs worse, as the theoretical performance guarantees of adversarial MAB algorithms are an order of magnitude
%\footnote{We preferred not to talk about \emph{regret} in this study, but in a few words: it is a measure of how \emph{bad} the algorithm performed in terms of its accumulated rewards, in comparison to the best possible policy, and should be as small as possible. For stochastic algorithms, being ``efficient'' means having a regret bounded as $R_T = \mathcal{O}(\log T)$, but for adversarial algorithms, it means having $R_T = \mathcal{O}(\sqrt{K T})$.}
worse than the one for stochastic ones.
% (in their respective case of application).
More is left on this aspect for our future work.

@@

% ---------- Bibliography ----------
%\begin{small}
\bibliographystyle{ieeetr}
\bibliography{biblio_RIoT}
%\end{small}

>>>>

Efficient Medium Access (MAC) policies allow devices to avoid interfering traffic and can significantly reduce the spectrum contention problem in unlicensed bands.
As end-devices battery life is a key constraint of IoT networks,
this leads to IoT protocols using as low signaling overhead as possible and simple ALOHA-based mechanisms.
%
In this Section, we analyze the performance of Multi-Armed Bandits (MAB) algorithms, used in combination with a time-frequency slotted ALOHA-based protocol.
We consider the Upper-Confidence Bound (\UCB) \cite{Auer02}, and the Thompson-Sampling (TS) algorithms \cite{Thompson33,AgrawalGoyal11,
Kaufmann12}.
% Both algorithms have already been applied with success, for Opportunistic Spectrum Access \cite{Jouini10} and recently for multi-users Cognitive Radio problems \cite{Toldov16}.

MAB learning has already been proposed in Cognitive Radio (CR) \cite{Haykin05}, and in particular, for sensing-based Dynamic Spectrum Access (DSA) in licensed bands \cite{Jouini10}.
For example, \cite{Jouini10} presents the OSA setting, and \cite{Maghsudi16} shows how MAB learning can be applied for small cell management in licensed 5G networks.
Recently, TS and \UCB{} algorithms have been used for improving the spectrum access in (unlicensed) WiFi networks \cite{Toldov16}, and the \UCB{} algorithm was used in a unlicensed and frequency- and time-slotted IoT network \cite{Bonnefoi17}.
Many recent works show that MAB algorithms work well for real-world radio signal.
However, even with only one dynamic user using the learning algorithm, the background traffic or the traffic of the other devices is never really stationary or \emph{i.i.d} (independent and identically distributed).
In recent works like \cite{Bonnefoi17}, several devices are using bandit algorithms, and the assumptions made by the stochastic bandit algorithms are not satisfied: as several agents learn simultaneously, their behavior is neither stationary nor \emph{i.i.d}.
As far as we know, we provide the first study to confirm robustness of the use of stochastic bandit algorithms for decision making in IoT networks with a large number of intelligent devices in the network, which makes the environment not stationary at all, violating the hypothesis required for mathematical proofs of bandit algorithms convergence and efficiency.

@@

% We now present the stochastic Multi-Armed Bandit (MAB) model,
% and the two stochastic MAB algorithms used in our experiments \cite{Bubeck12}.
While the stochastic MAB model has been used to describe some aspects of Cognitive Radio systems, it is in principle not suitable for our IoT model, due to the non-stationarity of the channels occupancy caused by the learning policy used by dynamic objects.
%Quite surprisingly, we will show in our experiments of Section~\ref{sub:41:numericalResults} that two algorithms inspired by the stochastic bandit modeling, UCB1 and Thompson Sampling, perform well even for coordinating multiple smart devices.

%This section presents the formalism of the Multi-Armed Bandit (MAB) problem, as introduced by \cite{LaiRobbins85}, and two classical algorithms designed to tackle its simplest version (stochastic MAB), \UCB{} from \cite{Auer02} and Thompson Sampling from \cite{Thompson33,Kaufmann12}.
%For more details, \cite{Bubeck12} is an excellent review.

@@

% In a Cognitive Radio application, arms model the \emph{channels}, and players are the \emph{dynamic end-devices}.
% For example in the classical OSA setting with sensing \cite{Jouini10}, a single dynamic device (a player) sequentially tries to access channels (the arms), and collects a reward of 1 if the channel is available %(as there is no primary user, we can assume the transmission to be successful),
% and 0 otherwise. So rewards represent the \emph{availability} of channels, and
% the parameter $\mu_k$ represents the mean availability of channel $k$.

@@

\paragraph{\emph{Adversarial} bandit algorithms?}
% \todo[inline]{Explain that we also tried adversarial algorithms ($\mathrm{Exp}3$), and it was working but less efficiently than \UCB{} and Thompson Sampling. Maybe add it on some curve?}
Instead of using MAB algorithms assuming a stochastic hypothesis on the system, we could try to use MAB algorithms designed to tackle a more general problem, that makes no hypothesis on the interfering traffic.
The \emph{adversarial MAB} algorithms is a broader family, and a well-known and efficient example is the $\mathrm{Exp}3$ algorithm \cite{Bubeck12}.
Empirically, the $\mathrm{Exp}3$ algorithm turned out to perform worse than both \UCB{} and TS in the same experiments.
%(see Section \ref{sub:41:numericalResults}).
Contrarily to the two stochastic algorithms, the use of $\mathrm{Exp}3$ is correctly justified, even in the non-stationary and non-\emph{i.i.d}, as its performance guarantee are true in \emph{any} setting.
But it is not so surprising that it performs worse, as the theoretical performance guarantees of adversarial MAB algorithms are an order of magnitude
%\footnote{We preferred not to talk about \emph{regret} in this study, but in a few words: it is a measure of how \emph{bad} the algorithm performed in terms of its accumulated rewards, in comparison to the best possible policy, and should be as small as possible. For stochastic algorithms, being ``efficient'' means having a regret bounded as $R_T = \mathcal{O}(\log T)$, but for adversarial algorithms, it means having $R_T = \mathcal{O}(\sqrt{K T})$.}
worse than the one for stochastic ones.
% (in their respective case of application).
More is left on this aspect for our future work.

@@

% % ---------- Bibliography ----------
% %\begin{small}
% \bibliographystyle{ieeetr}
% \bibliography{biblio_RIoT}
% %\end{small}

### 2019-02-14 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
I still don't have correct references...
Done for polishing references.

Multi-Armed Bandit (MAB) algorithms have been recently proposed as a solution to improve the performance of IoT networks and in particular in LPWAN \cite{Bonnefoi18,Azari18}.
In this paper, we describe the way we implemented a demo where we evaluate MAB algorithms, used in combination with a pure ALOHA-based protocol (such as the ones employed in LPWAN).
%
%\todo[inline]{Contributions et interets de la demo}
% MAB learning has already been proposed in Cognitive Radio (CR) \cite{Haykin}, and in particular, for sensing-based Dynamic Spectrum Access (DSA) in licensed bands \cite{Jouini}.
% Recently, TS and UCB{} algorithms have been used for improving the spectrum access in (unlicensed) WiFi networks \cite{Toldov}, and the UCB{} algorithm was used in a unlicensed and frequency- and time-slotted IoT network \cite{Bonnefoi}.
% Many recent works show that MAB algorithms work well for real-world radio signal.
% However, even with only one dynamic user using the learning algorithm, the background traffic or the traffic of the other objects is never really stationary or \emph{i.i.d.} (independent and identically distributed).
% In recent works like \cite{Bonnefoi}, several objects are using bandit algorithms, and the assumptions made by the stochastic bandit algorithms are not satisfied: as several agents learn simultaneously, their behavior is neither stationary nor \emph{i.i.d.}.
% As far as we know, we provide the first study to confirm robustness of the use of stochastic bandit algorithms for decision making in IoT networks with a large number of intelligent objects in the network, which makes the environment not stationary at all, violating the hypothesis required for mathematical proofs of bandit algorithms convergence and efficiency.
%
This demonstration is the first implementation which aims at assessing the potential gain of MAB learning algorithms in IoT scenarios.
% % even when the number of intelligent objects in the network increases, and the stochastic hypothesis is more and more questionable.
% To do that, we suppose an IoT network made of two types of objects: static objects that use only one channel (fixed in time), and dynamic objects that can choose the channel for each of their transmissions. Static objects form an interfering traffic, which could have been generated by objects using other standards as well.
% We first evaluate the probability of collision if dynamic objects randomly select channels (naive approach), and if a centralized controller optimally distribute them in channels (ideal approach).
% Then, these reference scenarios allow to evaluate the performance of UCB and TS algorithms in a decentralized network, in terms of successful communication rate, as it reflects the network efficiency.
% We show that these algorithms have near-optimal performance, even when the proportion of end-objects increases and the interfering traffic from other objects becomes less and less stochastic.
% \todo[inline]{(Remi) Si on parle de non stationarity, il faut donner un resultat a deux utilisateurs.}
Following our recent work presented in the previous Section~\ref{sec:4:firstModel}, we propose to model this problem as Non-Stationary\footnote{~Note that non-stationarity only comes from the presence of more than one dynamic object, as the background traffic is assumed independent and identically distributed \emph{i.i.d.}.} MAB.
We suggest to use low-cost algorithms, focusing on two well-known algorithms: a frequentist one (\UCB{}) and a Bayesian one (TS).
We consider the Upper-Confidence Bound (\UCB{}) \cite{Auer}, and the Thompson Sampling (TS) algorithms \cite{Thompson33}. Both algorithms have already been applied with success in the context of wireless decision making, both empirically for Opportunistic Spectrum Access \cite{Jouini},
and more recently for multi-users Cognitive Radio problems \cite{BessonALT18} with a more theoretical approach.

@@

The \UCB{} algorithm uses a parameter $\alpha > 0$, originally $\alpha$ was set to $2$ \cite{Auer}, but empirically $\alpha = 1/2$ is known to work better (uniformly across problems), and $\alpha > 1/2$ is advised by the theory \cite{bubeck2012regret}.
% This algorithm is simple to implement and use in practice, even on embedded micro-processors with limited computation and memory capabilities.
%
% \todo[inline]{Maybe in the implementation of UCB the $t$ $\log(t)$ should be the total amount of time the user tried to communicate? It is already the case, but we should say so.}
In our model, every dynamic end-user implements its own \UCB{} algorithm, \emph{independently}.
For one end-user, the time $t$ is the total number of sent messages from the beginning, as rewards are only obtained after a transmission.

@@

The TS algorithm, although being simple and easy to implement, is known to perform well for stochastic problems, for which it was proven to be asymptotically optimal \cite{AgrawalGoyal11,Kaufmann12}.
It is known to be empirically efficient, and for these reasons it has been used successfully in various applications, including on problems from Cognitive Radio \cite{Toldov,Mitton}, and also in previous work on decentralized IoT-like networks \cite{Darak16}.

@@

% ---------- Bibliography ----------
%\begin{small} % XXX small if needed?
\bibliographystyle{ieeetr}
\bibliography{biblio_RIoT}
%\end{small} % XXX small if needed?

>>>>

Multi-Armed Bandit (MAB) algorithms have been recently proposed as a solution to improve the performance of IoT networks and in particular in LPWAN \cite{Bonnefoi18,Azari18}.
In this paper, we describe the way we implemented a demo where we evaluate MAB algorithms, used in combination with a pure ALOHA-based protocol (such as the ones employed in LPWAN).
%
%\todo[inline]{Contributions et interets de la demo}
% MAB learning has already been proposed in Cognitive Radio (CR) \cite{Haykin05}, and in particular, for sensing-based Dynamic Spectrum Access (DSA) in licensed bands \cite{Jouini10}.
% Recently, TS and UCB{} algorithms have been used for improving the spectrum access in (unlicensed) WiFi networks \cite{Toldov16}, and the UCB{} algorithm was used in a unlicensed and frequency- and time-slotted IoT network \cite{Bonnefoi17}.
% Many recent works show that MAB algorithms work well for real-world radio signal.
% However, even with only one dynamic user using the learning algorithm, the background traffic or the traffic of the other objects is never really stationary or \emph{i.i.d.} (independent and identically distributed).
% In recent works like \cite{Bonnefoi17}, several objects are using bandit algorithms, and the assumptions made by the stochastic bandit algorithms are not satisfied: as several agents learn simultaneously, their behavior is neither stationary nor \emph{i.i.d.}.
% As far as we know, we provide the first study to confirm robustness of the use of stochastic bandit algorithms for decision making in IoT networks with a large number of intelligent objects in the network, which makes the environment not stationary at all, violating the hypothesis required for mathematical proofs of bandit algorithms convergence and efficiency.
%
This demonstration is the first implementation which aims at assessing the potential gain of MAB learning algorithms in IoT scenarios.
% % even when the number of intelligent objects in the network increases, and the stochastic hypothesis is more and more questionable.
% To do that, we suppose an IoT network made of two types of objects: static objects that use only one channel (fixed in time), and dynamic objects that can choose the channel for each of their transmissions. Static objects form an interfering traffic, which could have been generated by objects using other standards as well.
% We first evaluate the probability of collision if dynamic objects randomly select channels (naive approach), and if a centralized controller optimally distribute them in channels (ideal approach).
% Then, these reference scenarios allow to evaluate the performance of UCB and TS algorithms in a decentralized network, in terms of successful communication rate, as it reflects the network efficiency.
% We show that these algorithms have near-optimal performance, even when the proportion of end-objects increases and the interfering traffic from other objects becomes less and less stochastic.
% \todo[inline]{(Remi) Si on parle de non stationarity, il faut donner un resultat a deux utilisateurs.}
Following our recent work presented in the previous Section~\ref{sec:4:firstModel}, we propose to model this problem as Non-Stationary\footnote{~Note that non-stationarity only comes from the presence of more than one dynamic object, as the background traffic is assumed independent and identically distributed \emph{i.i.d.}.} MAB.
We suggest to use low-cost algorithms, focusing on two well-known algorithms: a frequentist one (\UCB{}) and a Bayesian one (TS).
We consider the Upper-Confidence Bound (\UCB{}) \cite{Auer02}, and the Thompson Sampling (TS) algorithms \cite{Thompson33}. Both algorithms have already been applied with success in the context of wireless decision making, both empirically for Opportunistic Spectrum Access \cite{Jouini10},
and more recently for multi-users Cognitive Radio problems \cite{Besson2018ALT} with a more theoretical approach.

@@

The \UCB{} algorithm uses a parameter $\alpha > 0$, originally $\alpha$ was set to $2$ \cite{Auer02}, but empirically $\alpha = 1/2$ is known to work better (uniformly across problems), and $\alpha > 1/2$ is advised by the theory \cite{Bubeck12}.
% This algorithm is simple to implement and use in practice, even on embedded micro-processors with limited computation and memory capabilities.
%
% \todo[inline]{Maybe in the implementation of UCB the $t$ $\log(t)$ should be the total amount of time the user tried to communicate? It is already the case, but we should say so.}
In our model, every dynamic end-user implements its own \UCB{} algorithm, \emph{independently}.
For one end-user, the time $t$ is the total number of sent messages from the beginning, as rewards are only obtained after a transmission.

@@

The TS algorithm, although being simple and easy to implement, is known to perform well for stochastic problems, for which it was proven to be asymptotically optimal \cite{AgrawalGoyal11,Kaufmann12}.
It is known to be empirically efficient, and for these reasons it has been used successfully in various applications, including on problems from Cognitive Radio \cite{Toldov16,Mitton16}, and also in previous work on decentralized IoT-like networks \cite{Darak16}.

@@

% % ---------- Bibliography ----------
% %\begin{small} % XXX small if needed?
% \bibliographystyle{ieeetr}
% \bibliography{biblio_RIoT}
% %\end{small} % XXX small if needed?

### 2019-02-14 2-Chapters/4-Chapter/IEEE_WCNC__2019__Paper__BMBM.git/IEEE_WCNC__2019__Paper__BMBM.tex
I still don't have correct references...
Done for polishing references.

In the context of Cognitive Radio \cite{Mitola99,Haykin05},
Multi-Arm Bandit (MAB) algorithms \cite{Auer,Auer02,Bubeck12} have been recently proposed as a potential solution for channel access in LPWA networks \cite{Bonnefoi18,Azari18,Bonnefoi17}.
We presented in Section~\ref{sec:4:firstModel} the impact of non-stationarity on the network performance using MAB algorithms is studied.
Low-cost algorithms following two well-known approaches, such as the Upper-Confidence Bound (\UCB{}) \cite{Auer,Auer02}, and the Thompson Sampling (TS) algorithms \cite{Thompson33} have reported encouraging results.
Other recent directions include theoretical analysis, like what we present in the next Chapter~\ref{chapter:5},
and realistic empirical simulations \cite{kumar2016two,kumar2017channel} or the previous Section~\ref{sec:4:gnuradio},
of the application of MAB algorithms for slotted wireless protocols in a decentralized manner,
or for instance applications to multi-hoping networks \cite{Mitton,Toldov}.
None of the above mentioned works discusses in detail the impact of retransmissions on the performance of MAB learning algorithms as we do now.

@@

Before presenting our proposed heuristics, we describe a \UCB{} bandit algorithm \cite{Auer}. It has reported to be efficient, while featuring a low complexity for its implementation. For this reason, it has been employed for IoT applications \cite{Bonnefoi17}, and we employ this approach to develop our proposals.

@@

\paragraph{Future works}
%
The utility and impact of the proposed approaches for LPWA networks motivates us to address several subjects as future works. Among them, the non-stationarity of the channel occupancy caused by the learning policy employed by the IoT devices.
%
For that end, modifications of MAB algorithms have been proposed, such as Sliding-Window-\UCB{} or Discounted-\UCB{} \cite{Garivier08}
or more recently M-\UCB{} \cite{CaoZhenKvetonXie18},
% or more recently GLR-\UCB{} \cite{Besson2019COLT},
that nevertheless have not been explored for the targeted problem.
Chapter~\ref{chapter:6} is focusing on this direction, but we did not have enough time to explore the possible applications of MAB policies designed for non-stationary problems to the model with retransmissions presented in this section.

@@

% ----------------------------------------------------------------------
\bibliographystyle{ieeetr}
\bibliography{IEEE_WCNC__2019__Paper__BMBM}

>>>>

In the context of Cognitive Radio \cite{Mitola99,Haykin05},
Multi-Arm Bandit (MAB) algorithms \cite{Auer02,Auer02,Bubeck12} have been recently proposed as a potential solution for channel access in LPWA networks \cite{Bonnefoi18,Azari18,Bonnefoi17}.
We presented in Section~\ref{sec:4:firstModel} the impact of non-stationarity on the network performance using MAB algorithms is studied.
Low-cost algorithms following two well-known approaches, such as the Upper-Confidence Bound (\UCB{}) \cite{Auer02,Auer02}, and the Thompson Sampling (TS) algorithms \cite{Thompson33} have reported encouraging results.
Other recent directions include theoretical analysis, like what we present in the next Chapter~\ref{chapter:5},
and realistic empirical simulations \cite{kumar2016two,kumar2017channel} or the previous Section~\ref{sec:4:gnuradio},
of the application of MAB algorithms for slotted wireless protocols in a decentralized manner,
or for instance applications to multi-hoping networks \cite{Mitton16,Toldov16}.
None of the above mentioned works discusses in detail the impact of retransmissions on the performance of MAB learning algorithms as we do now.

@@

Before presenting our proposed heuristics, we describe a \UCB{} bandit algorithm \cite{Auer02}. It has reported to be efficient, while featuring a low complexity for its implementation. For this reason, it has been employed for IoT applications \cite{Bonnefoi17}, and we employ this approach to develop our proposals.

@@

\paragraph{Future works}
%
The utility and impact of the proposed approaches for LPWA networks motivates us to address several subjects as future works. Among them, the non-stationarity of the channel occupancy caused by the learning policy employed by the IoT devices.
%
For that end, modifications of MAB algorithms have been proposed, such as Sliding-Window-\UCB{} or Discounted-\UCB{} \cite{Garivier08}
or more recently M-\UCB{} \cite{CaoZhenKvetonXie18},
% or more recently GLR-\UCB{} \cite{Besson2019GLRT},
that nevertheless have not been explored for the targeted problem.
Chapter~\ref{chapter:6} is focusing on this direction, but we did not have enough time to explore the possible applications of MAB policies designed for non-stationary problems to the model with retransmissions presented in this section.

@@

% % ----------------------------------------------------------------------
% \bibliographystyle{ieeetr}
% \bibliography{IEEE_WCNC__2019__Paper__BMBM}
